A Taxonomy of Twists of Supersymmetric Yang--Mills Theory

### 2022-04-19 paper_journal_edits.tex
fixed compilation error
rephrased remark

\begin{definition}
We say that a classical field theory $(E_N, \omega_N, S_N)$ on $N$ is a \defterm{dimensional reduction} along $p$ of the classical field theory $(E_M, \omega_M, S_M)$ on a manifold $M$ if one is given the data of a linear isomorphism $p^* E_N\cong E_M$ of the bundles of BV fields satisfying the following conditions:
\begin{itemize}
\item The diagram
\[
\xymatrix{
p^* E_N\otimes p^* E_N \ar^{\omega_N}[r] \ar^{\sim}[d] & p^*\Dens_N[-1] \ar^{\sim}[d] \\
E_M\otimes E_M \ar^{\omega_M}[r] & \Dens_M[-1]
}
\]
is commutative.
\item Via the projection map $p \colon M \to N$ we have $p^* S_N = S_M$ in $\oloc(\cE_M)$ (see the remark below).
\end{itemize}
\end{definition}

\begin{remark}
The last condition involves a pullback of local functionals.
Indeed, the isomorphisms $p^* E_N \cong E_M$ and $p^* {\rm Dens}_M \cong {\rm Dens}_N$ determine a map $p^* \colon \oloc(\cE_N) \to \oloc(\cE_M)$ defined as follows. 
First, we define a map
\[
p^* \colon \cO(\cE_{N,c}) \to \cO(\cE_{M,c}) 
\]
as the restriction of the map $\cE_{M, c}\rightarrow \cE_{N, c}$ given by integrating fields over the fibers of $p\colon M\rightarrow N$ which uses the fiberwise density provided by the isomorphism $p^*\Dens_N\cong\Dens_M$---these integrals are convergent due to the compact support condition.
Next, we use the natural embedding
\[\oloc(\cE_M)\subset \cO(\cE_{M, c})
\]
to interpret any local functional $S \in \oloc(\cE_M)$ as a functional on compactly-supported fields $\cE_{M,c}$. 
It is immediate to see that if $S$ is a local functional then so is $p^*S$ and hence we obtained the desired map.
\end{remark}

>>>>

\begin{definition}
We say that a classical field theory $(E_N, \omega_N, S_N)$ on $N$ is a \defterm{dimensional reduction} along $p$ of the classical field theory $(E_M, \omega_M, S_M)$ on a manifold $M$ if one is given the data of a linear isomorphism $p^* E_N\cong E_M$ of the bundles of BV fields satisfying the following conditions:
\begin{itemize}
\item The diagram
\[
\xymatrix{
p^* E_N\otimes p^* E_N \ar^{\omega_N}[r] \ar^{\sim}[d] & p^*\Dens_N[-1] \ar^{\sim}[d] \\
E_M\otimes E_M \ar^{\omega_M}[r] & \Dens_M[-1]
}
\]
is commutative.
\item Via the projection map $p \colon M \to N$ we have $p^* S_N = S_M$ in $\oloc(\cE_M)$.
\end{itemize}
\end{definition}

\begin{remark}
The isomorphisms $p^* E_N \cong E_M$ and $p^* {\rm Dens}_M \cong {\rm Dens}_N$ determine the pullback map
\[p^* \colon \oloc(\cE_N) \to \oloc(\cE_M)\]
of local functionals used in the last condition. Recall that one also has inclusion maps $\oloc(\cE_N)\hookrightarrow \cO(\cE_{N, c})$ and $\oloc(\cE_M)\hookrightarrow \cO(\cE_{M, c})$ allowing us to interpret local functionals as functionals on compactly-supported fields. Then there is a commutative diagram
\[
\xymatrix{
\oloc(\cE_N) \ar^{p^*}[r] \ar[d] & \oloc(\cE_M) \ar[d] \\
\cO(\cE_{N, c}) \ar[r] & \cO(\cE_{M, c})
}
\]
where the bottom map is the restriction under the map $\cE_{M, c}\rightarrow \cE_{N, c}$ given by integrating fields over the fibers of $p\colon M\rightarrow N$: this uses the fiberwise density provided by the isomorphism $p^*\Dens_N\cong\Dens_M$ and this is well-defined due to the compact support condition.
\end{remark}
